### 2013-10-07 src2/thesis.tex
hacking
apa
update

%stuff
\usepackage{latexsym}
\usepackage{tikz,pgflibraryshapes}
\usetikzlibrary{shapes,snakes,positioning}
\usepackage{pgfplots}
\usepackage{booktabs}
%%

@@

\section*{Acknowledgments}

@@

@@

\chapter{About this thesis}

\section{Papers}

The papers contained in this thesis falls in three different categories. 
\begin{itemize} 
\item General EDSL methodology in chapter~\ref{chap:EDSLImplementation}. 
\item GPU Programming using an EDSL in chapter~\ref{chap:GPUProgramming}. 
\item Retargetable parallel programming in chapter~\ref{chap:ArBB}. 
\end{itemize}

\subsection{EDSL implementation papers}

\subsubsection{\paperBB}

apa apa apa bepa cepa apa

\subsection{GPU Programming papers}

\chapter{Introduction}

\section{Plan} 
\begin{itemize} 
  \item The Scope
  \item The Problem 
  \item The Methods
  \item The Results 
\end{itemize}

\begin{itemize} 
  \item The Context
  \item Lift head from details 
  \item Why are there interesting questions around parallelism and GPUs
  \item The Story
  \item Reflect on leassons learnt along the way 
  \item Tell a story around the papers 
  \item Future Work
\end{itemize}

\clearpage{}
%\section*{Additional Publications}

%Papers not included in thesis

%\bibliographystyle{plain}
%\bibliography{intro}

@@

\bibliographystyle{plain}
\bibliography{thesis}
\addcontentsline{toc}{chapter}{Bibliography}

>>>>

%stuff
\usepackage{latexsym}
\usepackage{tikz,pgflibraryshapes}
\usetikzlibrary{shapes,snakes,positioning}
\usepackage{pgfplots}
\usepackage{booktabs}
%\usepackage{etoolbox}

\usepackage{multibib} 
\newcites{bb}{Bibliography} 
\newcites{ifl}{Bibliography}
\newcites{papp}{Bibliography}
\newcites{exp}{Bibliography}
\newcites{hl}{Bibliography}
\newcites{csort}{Bibliography}
\newcites{emb}{Bibliography}
\newcites{arbb}{Bibliography}
% \newcites{t}{Bibliography}
%\newcites[ifl}{Bibliography}

%\patchcmd{\thebibliography}{\section*}{\section}{}{}

\makeatletter
\renewenvironment{thebibliography}[1]
     {\section*{\bibname}%
      %\@mkboth{\MakeUppercase\bibname}{\MakeUppercase\bibname}%
      \list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother

%%

@@

% ---------------------------------------------------------------------------
%  ACKS !!! 
% ---------------------------------------------------------------------------
\section*{Acknowledgments}

@@

% ---------------------------------------------------------------------------
%  Guide for Oponent, grading committee
% ---------------------------------------------------------------------------
\section*{About this thesis}

The papers contained in this thesis falls in three categories. 
\begin{itemize} 
\item General EDSL methodology in chapter~\ref{chap:EDSLImplementation}. 
\item GPU Programming using an EDSL in chapter~\ref{chap:GPUProgramming}. 
\item Retargetable parallel programming in chapter~\ref{chap:ArBB}. 
\end{itemize} 
%In the following sections, each paper is given a short description. Hopefully 
%there is enough information to wet the apetite.

\subsection*{EDSL implementation papers}

\subsubsection*{\paperBB}

Authors: Josef Svenningsson and Bo Joel Svensson

\noindent We present a simple and compositional method for refication 
of monads (or compilation of a monadic embedded language). I implemented 
Obsidian using the method described here. The novelty and 
usefulness of this simple way to reify monads was recognised by Josef
and lead to the writing of this paper.

\subsection*{GPU Programming papers}

Authors: Bo Joel Svensson, Mary Sheeran and Koen Claessen \newline

Authors: Bo Joel Svensson, Koen Claessen and Mary Sheeran \newline

Authors: Koen Claessen, Mary Sheeran and  Bo Joel Svensson \newline

Authors: Josef Svenningsson, Bo Joel Svensson and Mary Sheeran \newline

Authors: Bo Joel Svensson and Mary Sheeran \newline
\noindent \emph{This work has not been published.}
\vspace{5mm}

In this paper the most recent additions and improvements of Obsidian are 
described.

Authors: Bo Joel Svensson and Ryan R. Newton

\noindent This position paper describes the work I did while on a 3 month internship at 
Intel. The main part of this work was implementation of Haskell bindings 
for the now retired Intel ArBB system.

The paper also describes work we did towards implementing a backend for the 
Accelerate system using ArBB. We reached a proof-of-concept implementation 
capable of running some simple Accelerate programs using the ArBB backend.
However, much work would remain to be able to run the full scope of Accelerate 
programs on ArBB.

Authors: Bo Joel Svensson and Mary Sheeran

\noindent Here we explore another way to provide the capabilities of ArBB to the 
Haskell programmer. Rather than trying to use ArBB as a backend to Accelerate 
we provide a more direct mapping of ArBB's functionality to Haskell idioms. 
Simply put, this means providing a more Haskell-programmer-friendly interface compared
to the raw ArBB bindings (which are a collection of functions in the IO monad).

\subsection*{Guide}

@@

% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
%
%  INTRODUCTION 
%
% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
\chapter{Introduction}

\section{The scope}

\noindent\emph{Data-Parallelism, Structured-Compositional programming}

\noindent\emph{GPUs}

\noindent\emph{The context, Lift head from details}

\subsection{Related work}

\noindent\emph{GPU Programmming languages}

\noindent\emph{data-parallel programming languages}

\noindent\emph{Embedded languages}

\noindent\emph{Monad reification methods}

\section{The problem}

\emph{what is so interesting about Parallelism and GPUs}

\section{The method}

\noindent\emph{Obsidian, Embedded languages}

\noindent\emph{Array representations}

\noindent\emph{Compositionality}

\noindent\emph{Hierarchies}

\section{The results}

\emph{ How well did we do?}

\section{Future work}

\noindent\emph{Find a niche for Obsidian}

\noindent\emph{Improve on Warp level capabilities}

\noindent\emph{Improve expressivity, code performance}

\section{Discussion}

\clearpage{}

% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
%
%  PAPERS 
%
% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %

@@

% ---------------------------------------------------------------------------
% nocites 
% ---------------------------------------------------------------------------
\nocite{*}

\makeatletter
\renewenvironment{thebibliography}[1]
     {\chapter*{\bibname}%
      \@mkboth{\MakeUppercase\bibname}{\MakeUppercase\bibname}%
      \list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
       \endlist}
\makeatother

\bibliographystyle{alpha}
\bibliography{thesis}
\addcontentsline{toc}{chapter}{Bibliography}
